---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MiAF

<!-- badges: start -->
<!-- badges: end -->

The goal of MiAF is to test for overall association between the composition of a microbial community
             and a host phenotype of interest (e.g. disease status) with/without covariate adjustments. 
             In this package, we construct a novel community-level test, named MiAF,
             by adaptively combining p-values from OTU-level (univariate) tests.

## Installation

``` r
library(devtools)
install_github("songbiostat/MiAF")
```

## Arguments

* Y: a numeric vector for continuous or binary responses.
* X: a matrix of the OTU table.
     Row - samples, column - OTUs.
* tree: a rooted phylogenetic tree of R class "phylo".
* cov: a data frame/matrix for covariate adjustment
  Row - samples, column - covariates.
* model: "gaussian" is for the linear regression model (continuous);
  "binomial" is for the logistic regression model (binary).
* n.perm: the number of permutations.

## Values

* UniFrac: unweighted UniFrac-like test p-value.
* wUniFrac: weighted UniFrac-like test p-value.
* UniFrac5: generalized UniFrac-like test p-value.
* tip.abun: leaf-nodes-only test p-value.
* com: p-value of MiAF test that combines p-values of the above four tests.
* select:a list of selected associated taxa.
    + lower: under-presented taxa based on lower-tail p-values.
    + upper: over-presented taxa based on upper-tail p-values.

## Example

```{r example, eval=FALSE}
library(MiAF)
library(GUniFrac)
data(throat.otu.tab)
data(throat.meta)
data(throat.tree)

y <- as.numeric(throat.meta$SmokingStatus == 'Smoker')
gender <- as.numeric(throat.meta$Sex == 'Female')
zcov <- as.matrix(gender)
MiAF(Y = y, X = throat.otu.tab, tree = throat.tree, cov = zcov, model = "binomial", n.perm = 999)
```

